\section{Atomic Layer Deposition}
\subsubsection{Aim}
To lay down a thin, controlled layer of \ce{Al2O3} or \ce{HfO}.

\subsubsection{Steps}
\begin{enumerate}
\item Open up the Savannah software on the laptop.
\item Check that the inner and outer wafer stage heaters are set to \SI{120}{\degreeCelsius}, and that the stages
are at that temperature. (note: \ce{N2} flow should be at 5 sccm) Chamber will not vent if the stage is at $<\SI{80}{\degreeCelsius}$.
\item Hit the \fbox{Vent} button to vent the deposition chamber. Wait until the software says vented.
\item Open lid using heat-proof handle and load wafers. Close chamber and hit the \fbox{Pump} button to pump down chamber.
\item Adjust the wafer stage temperature to the desired range (\SI{80}{\degreeCelsius}---\SI{200}{\degreeCelsius}).
\item Load a recipe by right-clicking in the recipe panel. Standard recipes are defined for \ce{Al2O3} and \ce{HfO} for several temperatures.
\item Adjust the number of cycles to get the desired thickness. Growth rates are given in the ALD Handbook which should be near the system.
\item Run recipe by pressing \fbox{Run}
\item Once recipe is complete, temperature should be back at \SI{120}{\degreeCelsius} and \ce{N2} flow at 5 sccm. Press \fbox{Vent} to vent chamber.
\item Unload samples (remember the heat-proof handle) and restore chamber vacuum by pressing \fbox{Pump}.
\item Update logbook
\end{enumerate}

\subsubsection{Liftoff}
Liftoff of ALD has in the past been slightly tricky to achieve. The following parameters have been successful in the past.
\begin{enumerate}
\item \textbf{Resist: } Spin either AZ6612 (positive) or nLOF2020 (negative). Bilayer resist stacks do not seem to help with liftoff, I would avoid them.
\item \textbf{Liftoff: } Leave chips overnight in NMP, or for as long as one can be bothered to leave them. After the break, sonicate for 20s on medium power
    and spray with IPA. Leave in NMP for 5 more minutes and then clean and dry chip.
\end{enumerate}

\subsubsection{Misc}
\begin{enumerate}
\item If the chamber doesn't vent, ensure that the stage heaters are on.
\item Each cycle will deposit about \SI{1}{\angstrom} of dielectric and takes about 1:20 minutes. A \SI{20}{\nano\meter} layer
will take a little over \SI{4}{\hour} to complete.
\item It is worth checking that the first few cycles work as the precursors may have been exhausted. If this is the case, notify Gordon to get them replaced.
\end{enumerate}
\newpage

