\section{\ce{O2} Plasma Ashing}
\subsubsection{Aim}
Remove organic contaminants and resist remnants on the surface of the device

\subsubsection{Needs}
\begin{itemize}[noitemsep]
  \item Chip with developed resist
\end{itemize}

\subsubsection{Steps}
\begin{enumerate}
  \item Turn on the \boxed{\ce{N2}~Purge} switch to begin nitrogen flowing (even if already vented).
  \item Open chamber (door should open easily) and place chips onto the glass sample stage.
  \item Close the chamber door and turn on mechanical pump switch while firmly pushing against the door. Note that
  the \boxed{\ce{N2}~Purge} switch should still be on and should be left on. It will automatically turn off when the pump starts.
  \item Wait until the chamber pressure is $< \SI{85}{\milli\torr}$ (approx 15 mins). Note, $< \SI{70}{\milli\torr}$ is ideal.
  \item Flick the \boxed{GAS1~Oxygen} switch to on and wait for pressure in chamber to stabilize. It should come up to $\approx\SI{340}{\milli\torr}$.
  \item If necessary adjust the needle valve to bring the \ce{O2} pressure into the correct range. Note: very sensitive.
  \item Check \boxed{Local~Enable} is {\em on} and \boxed{Power~Control} is set to {\em Internal}.
  \item Press \boxed{Power~Line~On} button (yellow).
  \item Set up a hand held timer for the correct time (\SI{30}{\second} for PMMA, \SI{60}{\second} for optical).
  \item Press \boxed{RF~ON} to start the plasma and start the timer.
  \item Check RF power is $\approx\SI{50}{\watt}$ and reflected power is $< \SI{1}{\watt}$. If necessary, adjust power or Tuning/Loading
    to bring parameters in range.
  \item Press \boxed{RF~OFF} to stop ashing once time has expired.
  \item Press \boxed{Power~Line~On} button again to turn power supply off, wait until the yellow light fades (can take up to 1 minute).
  \item Turn off oxygen. Wait until vacuum has recovered to below $\approx\SI{100}{\milli\torr}$.
  \item Turn off mechanical pump. \ce{N2} should automatically start. Unlatch the door, once venting is complete it should pop open.
  \item Remove samples. Close the door and turn off \boxed{\ce{N2}~Purge} switch.
  \item Record results in log book
\end{enumerate}

\newpage

